Dissertation

### 2024-10-12 Manuscript/manuscript.qmd
initial re-render with inclusion of acknowledgement and abstract

```{r}
#| label: fig-ex-design1
#| fig-width: 10
#| fig-height: 6
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
#| cache: false
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
  ggh4x,htmltools,future,furrr,ez)

>>>>

```{r}
#| label: fig-ex-design1
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
#| cache: false
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
  ggh4x,htmltools,future,furrr,ez)

### 2024-10-12 Sections/Introduction.qmd
initial re-render with inclusion of acknowledgement and abstract

```{r}
#| label: fig-ex-design1
#| fig-width: 10
#| fig-height: 6
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
pacman::p_load(dplyr, ggplot2, patchwork)

>>>>

```{r}
#| label: fig-ex-design1
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
pacman::p_load(dplyr, ggplot2, patchwork)

### 2024-10-12 Sections/full.qmd
initial re-render with inclusion of acknowledgement and abstract

```{r}
#| label: fig-ex-design1
#| fig-width: 10
#| fig-height: 6
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
#| cache: false

>>>>

```{r}
#| label: fig-ex-design1
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
#| cache: false

### 2024-10-12 index.qmd
start the revisions page. Updates to main paper files from the HTW updates I did awhile ago.
initial re-render with inclusion of acknowledgement and abstract

---
title: "Dissertation"
author:
- name: Thomas E. Gorman
  affiliation: Indiana University
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  orcid: 0000-0001-5366-5442
comments: false
date-format: 'MMM YYYY'
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 1400px
      margin-width: 170px
      gutter-width: 1.5rem
    self-contained: false
---

@@

>>>>

---
title: "Dissertation"
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
comments: false
date: today
#date-format: 'MMM YYYY'
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 1400px
      margin-width: 170px
      gutter-width: 1.5rem
    self-contained: false
---

@@

##

-----

[Revisions](revisions.qmd)
